Project Notes - Quality Measurement

### 2020-02-15 StateOfPractice/Peter-Notes-QualityMeasurement.tex
peter's notes - cleaned up, added metrics to reusability, portability

\subsubsection{Metrics}
\subsubsection{Notes}
Measuring Software Reusability (Poulin)\\

Taxonomy of reusability mctrics
1. Empirical methods
-
-
Module oriented
- Complexity based
- Size based
- Reliability based
Component oriented

 2.Qualitative methods
-
-Module oriented
- Style guidelines
Component oriented
- Certification guidelines
- Quality guidelines\\

3.1 Prieto-Diaz and Freeman:
Their process model encourages
white-box reuse and consists of finding candidate
reusable modules, evaluating each, deciding which
module the programmer can modify the easiest, then
adapting the module. In this model they identify
four module-oricntcd metrics and a fifth metric used
to modify the fust four.

Program size. Reuse depends on a small module
size, as indicated by lines of source code.
Program structure. Reuse depends o n a simple
program structure as indicated by fewer links to
other modules (low coupling) and low
cyclomatic complexity.
Program documentation.
Reuse depends on
excellent documentation as indicated by a sub-
jective overall rating o n a scale of 1 to 10.
Programming language. Reuse depends on pro-
gamming language to the extent that it helps to
reuse a module written in the same programming
language. If a reusable module in the same lan-
guage does not exist, the degree of similarity
between the target language and the one used in
the module affects the difficulty of modifying the
module to meet the new requirement.
Reuse experience. The experience of the reuser
in the programming language and in the appliea-
tion domain affects the previous metrics because
every programmer views a module from their
own perspective. For example, programmers
wtll have diffcrent views of what makes a
“small” module, depending on their background.
?’lis fifth metric serves to modify the values of
the other mctrics.

-----

Chidamber and Kemerer object-oriented metrics:\\

https://www.aivosto.com/project/help/pm-oo-ck.html:\\

eg weighted methods per class, number of children, coupling per class\\

Software reusability metrics estimation: Algorithms, models and optimization techniques (Padhy)\\

Cyclomatic complexity: independent paths through source code\\

Software Reuse and Reusability Metrics and Models (Frakes, Terry)\\

A new reusability metric for object-oriented software (Barnard)\\

A metrics suite for measuring reusability of software components (Washizaki)\\

Reusability Index: A Measure for Assessing Software Assets Reusability (Ampatzoglou)

~\newpage
\subsection{Portability}
\subsubsection{Definition}
Effort required to transfer a program between system environments (including hardware and software).\\
\subsubsection{Metrics}
\subsubsection{Notes}
compare effort to port to effort to redevelop\\

@@

Issues in the Specification and Measurement of Software Portability (Mooney):\\
The term portability
 refers to the ability of a software
 unit to be ported (to a given environment).
 A program is
 portable if and to the degree that the cost of porting is less than
 the cost of redevelopment. A software unit would be perfectly
 portable if it could be ported at zero cost, but this is never
 possible in practice.
 Instead, a software unit may be
 characterized by its degree ofportability,
 which is a function of
 the porting and development costs, with respect to a specific
 target environment.\\

@@

Designing a Measurement Method for the Portability Non-functional Requirement (Talib):\\
 EffortNew is the total effort needed in working hours units
 to develop the software functionalities on a new
 environment\\

-----------\\
https://www.softwaretestinghelp.com/what-is-portability-testing/:\\

>>>>

\subsubsection{Metrics}
\noindent Poulin (non-direct source):
\begin{enumerate}
	\item Size\\

	Count lines of source code.
	\item Structure\\

	Count links to other modules.
	\item Documentation\\

	Subjective rating on a scale of 1 to 10.
	\item Language\\

	Subjective rating based on how common the language is.
	\item Simple interfaces\\

	Count the average number of passed variables to modules.
	\item Few calls to other modules\\

	Count the average number of calls to other modules.
	\item Cyclomatic complexity\\

	Measure cyclomatic complexity
	\item Self descriptiveness\\

	Measure average percentage of comment lines in module
	\item Number of problem reports\\

	Measure average number of outstanding defects in the module.
\end{enumerate}

\noindent Chidamber and Kemerer:
\begin{enumerate}
	\item Methods per class\\

	Measure the average number of methods defined in each class (want to keep low).
	\item Number of children\\

	Measure the number of immediate child classes derived from a base class (wan this to be high). 
	\item Coupling between object classes\\

	Measure the average number of methods or variables per class that are used by other classes (want to keep this low).
\end{enumerate}

\noindent Software reusability metrics estimation: Algorithms, models and optimization techniques (Padhy):\\ 
\begin{enumerate}
	\item Methods per class (WMC)\\

	Measure the number of methods per class.
	\item Depth of inheritance tree (DIT)\\

	Measure the highest length from the rood to the node.
	\item Number of children (NOC)\\

	Measure the average total number of total number of sub-classes.

	\item Method complexity (MC)\\

	Measure the average total number of methods present in a class.
\end{enumerate}

\noindent A new reusability metric for object-oriented software (Barnard):\\ 
\begin{enumerate}
	\item Coupling (calls to foreign classes)
	\item Number of methods
	\item Number of attributes
	\item Meaningful name
	\item Documentation
	\item Lines of code
	\item Comment lines
	\item Depth of inheritance
	\item Number of children
	\item Cohesion 
	\item Class variables
	\item Complexity of data structure
	\item Interface parameters
	\item Calls to foreign classes
	\item Calls to library classes
	\item Access (public, protected, private)
\end{enumerate}

\noindent Reusability Index: A Measure for Assessing Software Assets Reusability (Ampatzoglou):\\ 
\begin{enumerate}
	\item Number of classes in a module
	\item Number of properties
	\item Interface complexity
	\item Documentation quality
	\item Number of open bugs
\end{enumerate}

\subsubsection{Notes}
\noindent Measuring Software Reusability (Poulin)\\

Taxonomy of reusability metrics:\\
1. Empirical methods:\\
Module oriented (complexity based, size based, reliability based), 
Component oriented\\

2.Qualitative methods:\\
Module oriented (style guidelines), Component oriented (certification guidelines, quality guidelines)\\

\noindent Chidamber and Kemerer object-oriented metrics (https://www.aivosto.com/project/help/pm-oo-ck.html):\\
The Chidamber and Kemerer metrics suite originally consists of 6 metrics calculated for each class: WMC, DIT, NOC, CBO, RFC and LCOM1. The original suite has later been amended by RFC´, LCOM2, LCOM3 and LCOM4 by other authors.\\

\noindent Software reusability metrics estimation: Algorithms, models and optimization techniques (Padhy)\\

\noindent A new reusability metric for object-oriented software (Barnard)\\

\noindent Reusability Index: A Measure for Assessing Software Assets Reusability (Ampatzoglou)

~\newpage
\subsection{Portability}
\subsubsection{Definition}
Effort required to transfer a program between system environments (including hardware and software).\\
\subsubsection{Metrics}
Same as installability?
\begin{enumerate}
	\item Time to port
	\item OS platforms
	\item OS versions
	\item Hardware platforms
	\item Number of external libraries needed
\end{enumerate}

\subsubsection{Notes}
compare effort to port to effort to redevelop\\

@@

\noindent Issues in the Specification and Measurement of Software Portability (Mooney):\\
The term portability
 refers to the ability of a software
 unit to be ported (to a given environment).
 A program is
 portable if and to the degree that the cost of porting is less than
 the cost of redevelopment. A software unit would be perfectly
 portable if it could be ported at zero cost, but this is never
 possible in practice.
 Instead, a software unit may be
 characterized by its degree ofportability,
 which is a function of
 the porting and development costs, with respect to a specific
 target environment.\\

@@

  The principal types of portability usually considered are binary portability (porting the executable form) and source portability (porting the source language representation). Binary portability offers several advantages, but is possible only across strongly similar environments.Source portability assumes availability of source code, but provides opportunities to adapt a software unit to a wide range of environments.  In this paper we consider only source portability.The porting process has two principal components which we call transportation and adaptation.  Transportation is physical movement;  this may not be trivial since compatible media must be used and various types of representation conversion may be required.  Adaptation is any modification that must be performed on the original version;  we take this to mean both mechanical translation such as by language processors, and manual modification by humans\\

\noindent Designing a Measurement Method for the Portability Non-functional Requirement (Talib):\\

\noindent https://www.softwaretestinghelp.com/what-is-portability-testing/:\\
